Species motif participation provides unique information about species risk of extinction

### 2023-04-18 manuscript/supplement_motifs.tex
fixed one more SI fig

    Motif participation varies with global-scale network properies.
    % Updated with network-level random effect
    \begin{table}[hb!]
        \centering
        \caption{Motif participation varies with size and connectance. Here we give the range and mean proportion of each motif in species' motif participation vectors. 
        We also show the coefficients ($\beta$) for network size (S), connectance (C), and their interaction in general linear models predicting the proportion of each motif in a participation vector.
        Coefficients in \textbf{bold} are significant ($\alpha$=0.05).
        We also show the coefficients for similar models relating the proportion of each motif to in-degree or trophic level.
        All models were fit with a binomial error distribution and logit link function.
        Predictors were not centered or standardized before model fitting. Motifs are ordered according to mean proportion.}
        % Relevant lms are pchainlm, pomnilm, papplm, pdirlm}
        \label{tab:partic_vs_SC}   
        \footnotesize
        \begin{tabular}{c|c c c | c c c | c | c}
            Motif & Min & Max & Mean & S & C & Int. & in-Deg & TL \\
            \hline
            3-sp Chain & 0 & 1 & 0.249 & \textbf{1.20$\times10^{-3}$} &  -0.652 & \textbf{-1.77$\times10^{-2}$} & \textbf{-6.99$\times10^{-3}$} & \textbf{9.84$\times10^{-2}$} \\
            App. Comp & 0.250 & 0.765 & 0.422 & \textbf{-1.82$\times10^{-3}$} & \textbf{-3.18} & 6.92$\times10^{-3}$ & \textbf{-8.76$\times10^{-3}$} & \textbf{2.40$\times10^{-1}$}\\
            Dir. Comp & 0.0501 & 0.359 & 0.179 & -1.18$\times10^{-3}$ & \textbf{-4.50} & \textbf{4.79$\times10^{-2}$} & \textbf{-1.43$\times10^{-3}$} & \textbf{-2.52$\times10^{-1}$} \\
            Omnivory & 0.006 & 0.346 & 0.164 & \textbf{3.64$\times10^{-3}$} & \textbf{12.5} & \textbf{-4.19$\times10^{-2}$} & \textbf{2.29$\times10^{-2}$} & \textbf{-2.27$\times10^{-1}$}\\   
            \hline
            \end{tabular}
            \end{table}

    \begin{figure}[ht!]
        \centering
        \includegraphics[width=.9\textwidth]{figures/participation_vs_SC.eps}
        \caption{The proportion of each motif in a consumer's participation vector varied sigificantly with connectance but not with network size or the interaction between size and connectance. Because the interaction was not significant, we show relationships for intermediate values of size and connectance when plotting against the other variable. These relationships were steepest for apparent competition and omnivory.}
        \label{fig:roles_vs_SC}
    \end{figure}

>>>>

    \begin{table}[hb!]
        \centering
        \caption{Motif participation varies with size and connectance. Here we give the range and mean proportion of each motif in species' motif participation vectors. 
        We also show the coefficients ($\beta$) for network size (S), connectance (C), and their interaction in general linear models predicting the proportion of each motif in a participation vector.
        Coefficients in \textbf{bold} are significant ($\alpha$=0.05).
        We also show the coefficients for similar models relating the proportion of each motif to in-degree or trophic level.
        All models were fit with a binomial error distribution and logit link function.
        Predictors were not centered or standardized before model fitting. Motifs are ordered according to mean proportion.}
        % Relevant lms are pchainlm, pomnilm, papplm, pdirlm}
        \label{tab:partic_vs_SC}   
        \footnotesize
        \begin{tabular}{c|c c c | c c c | c | c}
            Motif & Min & Max & Mean & S & C & Int. & in-Deg & TL \\
            \hline
            3-sp Chain & 0 & 1 & 0.249 & \textbf{1.20$\times10^{-3}$} &  -0.652 & \textbf{-1.77$\times10^{-2}$} & \textbf{-6.99$\times10^{-3}$} & \textbf{9.84$\times10^{-2}$} \\
            App. Comp & 0.250 & 0.765 & 0.422 & \textbf{-1.82$\times10^{-3}$} & \textbf{-3.18} & 6.92$\times10^{-3}$ & \textbf{-8.76$\times10^{-3}$} & \textbf{2.40$\times10^{-1}$}\\
            Dir. Comp & 0.0501 & 0.359 & 0.179 & -1.18$\times10^{-3}$ & \textbf{-4.50} & \textbf{4.79$\times10^{-2}$} & \textbf{-1.43$\times10^{-3}$} & \textbf{-2.52$\times10^{-1}$} \\
            Omnivory & 0.006 & 0.346 & 0.164 & \textbf{3.64$\times10^{-3}$} & \textbf{12.5} & \textbf{-4.19$\times10^{-2}$} & \textbf{2.29$\times10^{-2}$} & \textbf{-2.27$\times10^{-1}$}\\   
            \hline
            \end{tabular}
            \end{table}

    \begin{figure}[ht!]
        \centering
        \includegraphics[width=.9\textwidth]{figures/participation_vs_SC.eps}
        \caption{The proportion of each motif in consumer's participation vectors varied with connectance, network size, and their interaction (except for apparent competition). We show relationships for the smallest and largest values of network size (S) and connectance (C).}
        \label{fig:roles_vs_SC}
    \end{figure}
